---
title: "Weight of Fish"
author: "Melany Vasquez"
date: "Summer 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
allthat <- read.csv(file = "Fish.csv")
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

# Perch

```{r}
perch <- filter(allthat,Species == "Perch")
perch <- select(perch,-1)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

In the model perch it shows that the best two plots to use to find the weight is to use height and width.


```{r}
which.max(summary.out$adjr2)
```

Using two variables.

```{r}
summary.out$which[2,]
```

This model suggests that represents the fish species Perch, summarizes that the best two variables for the models were height and width.


# Bream

```{r}
Bream <- filter(allthat,Species == "Bream")
Bream <- select(Bream,-1)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best two variables to use is Length 2 and Height.

```{r}
which.max(summary.out$adjr2)
```

using three variables.

```{r}
summary.out$which[2,]
```
This model suggests that represents the fish species Bream, summarizes that the best two variables to use is length 2 and height.


# Smelt

```{r}
Smelt <- filter(allthat,Species == "Smelt")
Smelt <- select(Smelt,-1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smelt,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best two variables for Smelt in this model is Length 2 and Width.


```{r}
which.max(summary.out$adjr2)
```
using four variables.

```{r}
summary.out$which[2,]
```
This model suggests that represents the fish species Smelt, summarizes that the best two variables are length 2 and Width.


#  conclusion

To conclude, The way we went along to figure out and respond to building the best regression model and pick out the best one. After organizing the data file Fish.csv I was able to conclude That the best regression model that was also summarized was the last model which specified over the fish species "Smelt". This model presented that it used four variables and suggested that the best two variables were length 02  and width. I was able to figure out the summaries by using the helper file named Bestsubset_Regression.
